Direction-Free In-Air Signature Verification Using WIFI CSI Signal

### 2019-04-17 190410_Paper_ACPR/paper_v0.tex
latex: setting

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
%\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Direction-Free In-Air Signature Verification Using WIFI CSI Signal\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

@@

\section{Proposed System}
\subsection{Data Acquisition and Preprocessing}
Gathering CSI signal, Make CSI Image
\subsection{Siamese Network For Verification}
i. Feature Extraction
- Symmetric CNN Architecture
® Symetric : Share Weights
◊ To extract the same characteristics from signals in different directions.
® CNN: Feature Extractor
◊ Automatically extract feature vector from CSI image
ii. Feature Matching
Use L1 distances of Feature vector of 2 input images

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Direction-Free In-Air Signature Verification Using WIFI CSI Signal}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Young Woong KWON\inst{1} \and
JooYoung KIM\inst{1} \and
Kar-Ann TOH\inst{1}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Yonsei University \and
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

@@

\section{Proposed System}
\subsection{Data Acquisition and Preprocessing}
In this section, we introduce a system for recognition of Wi-Fi based in-air signature which utilizes the Siamese network learning for validation.
An overview of the proposed scheme is shown in Fig.1.
\begin{figure}
\includegraphics[width=\textwidth]{methods1.eps}
\caption{...} \label{method1}
\end{figure}

 Two preprocessed signals enter the Siamese network and the network 
extracts non-directional characteristics from two signals and calculates how similar the two extracted characteristics are.
 The output of the Siamese network is 1 when the distance of the characteristic vector is close, and 0 when it is far.
the network is learned by the back-propagation.

The main purpose of this system is to receive two csi signals as input, to determine if the two signals are the same signature.
Since signals may differ in the direction in which they are entered, our system must be capable of extracting non-direction-related characteristics from two signals.

In order to be used as an input to a siamese network, the data must be pre-processed.

First, the signal have to converted to non-complex form.
Since the Wi-Fi signature signals in CSI packets in 2.4Ghz has firmware issues in their phase[ref] we used absolute of signal only.

Second, all inputs must be arranged of same size.
Since all signals have different length, the gradient operation with respect to the time instance is adopted to measure the short time energy. 
Data points with the highest short-time energy within the time period are regarded as the starting and the ending points of the in-air signature.
And they are re-sampled uniformly based on Fast Fourier Transform (FFT) [16] to normalize the length of the data.

\subsection{Siamese Network For Verification}
The model receives two processed CSI signals as inputs, and outputs the probability that the two signals are of the same class as the output.

Even if a signal belongs to the same class, the shape of the input is very different if the signal is oriented differently.
To classify regardless of the direction of the signal, the model shall be capable of extracting features unrelated to the direction.
\subsection{Feature Extraction}
When two processed signals come as the input, they are put to 2 symmetric CNN network.

Purpose of CNN is to extract features from signal.
By sharing their feature map, this CNN networks is trainin to learn characteristics regardless of the direction only.

To perform the feature extraction, we firstly need to have a convolutional neural networks  to serve as the feature extractor
Based on the ConvNet structure [17] the feature extractor of the proposed pretraining model consists of i convolution layers and activation functions followed by i max-pooling layers. Each convolution layer has f∗ filters to be trained, where ∗ = 1, ..., i. In a similar manner, j fully connected layers constitute the classifier of pretraining model where each layer has g•,(•=1,...,j) neurons to be trained.

\subsection{Feature Matching}
Output of the CNN are feature vectors extracted from two samples. The Euclidean distance between the two features can be calculated.
In the proposed system, this Euclidean distance is utilized to match between two feature vectors.

\subsection{Loss and Backpropagation}
 We impose a regularized cross-entropy objective on our binary classifier.
This objective is combined with standard backpropagation algorithm, where the gradient is additive across the twin networks due to the tied weights.
 We initialized all network weights in the convolutional layers from a normal distribution with zero-mean and a standard deviation of 10−2. Biases were also initialized from a normal distribution, but with mean 0.5 and standard deviation 10−2.
\begin{figure}
\includegraphics[width=\textwidth]{network1.eps}
\caption{...} \label{network1}
\end{figure}
